Reproducible Results in Parsing-Based Machine Translation:\\ The JHU Shared Task Submission

### 2010-04-23 papers/wmt10.pipeline/paper.tex
working on figure
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1603 0ae5e6b2-d358-4f09-a895-f82f13dd62a4
Possibly final draft
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1618 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

\documentclass[11pt]{article}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{tikz}
\usetikzlibrary{fit,shapes.misc,shapes}
\usepackage{acl2010}
%\usepackage[colorinlistoftodos]{todonotes}

@@

\begin{figure*}[htbp]
\include{figure.pgf}
\caption{Machine translation workflow. Nodes in grey indicate software and scripts. The scripts and configuration files used to implement and run this workflow are available for download at \url{http://sourceforge.net/projects/joshua/files/joshua/1.3/wmt2010-experiment.tgz}}
\label{dependencyGraph}
\end{figure*}

@@

The Z-MERT implementation \cite{Zaidan2009} of minimum error rate training \cite{Och2003c} was used for parameter tuning. Tuned grammars were used by Joshua to translate all test sets. The Joshua decoder produces n-best lists of translations.

>>>>

\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{tikz}
\usetikzlibrary{fit,shapes.misc,shapes}
\usepackage{acl2010}
%\usepackage[pdftex]{graphicx}
%\usepackage[colorinlistoftodos]{todonotes}

@@

\begin{figure*}[htbp]
\include{figure.pgf}
\caption{Machine translation workflow. Square nodes in grey indicate software and scripts. The scripts and configuration files used to implement and run this workflow are available for download at \url{http://sourceforge.net/projects/joshua/files/joshua/1.3/wmt2010-experiment.tgz}}
\label{dependencyGraph}
\end{figure*}

@@

The Z-MERT implementation \cite{Zaidan2009} of minimum error rate training \cite{Och2003c} was used for parameter tuning\footnote{Z-MERT seed value was set to 12341234}. Tuned grammars were used by Joshua to translate all test sets. The Joshua decoder produces n-best lists of translations.
